---
title: "Examples and tests for the `cepaea_parser()` function"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
```

We load the function:

```{r}
source("cepaea_parser.R")
```

We create a vector that contains various valid and invalid *Cepaea* phenotypes:
```{r}
stringtest <- c("Y12345",
                "P123(45)",
                "P(123)(45)",
                "B00000",
                "Y00345",
                "PY12:45",
                "DP12.45",
                "DZ12685",
                "Z12345",
                "P123",
                "Y123450"
                )
```


```{r}
cepaea_parser(stringtest)
```
The function will output a data frame with various columns describing separate elements of the phenotype. If an error is detected in one individual string, the function will output `NA`s for all columns for that individual, rather than trying to guess which correct-looking elements of the string are indeed correct. It will also warns the user, so that they can check their records.


When all the elements in the input are invalid, the function throws an error instead of a warning:

```{r}
cepaea_parser("X12345")
```

```{r}
cepaea_parser(c("Y123","Z12345"))
```

```{r}
cepaea_parser("Y12678")
```

